Sushi monster

### 2025-02-23 inst/ordertable_to_ranktable.Rmd
whitespace typo
S3 classes ordertable and ranktable

# Toy dataset

@@

Note that it is possible to view object `RT` directly by removing
class `ranktable`:

```{r viewdirect}
class(RT)
class(RT) <- "matrix"  # removes "ranktable" from class list
RT
```

Note carefully that the second row of `RT` (which corresponds to the
second judge) does *not* match the second column of `OT`.  The way to
read the second row of `RT` is as follows.  We see the entries `1 3 4
5 2` indicating that the first choice was competitor 1 [viz `a`], the
second choice was competitor 3 [viz `c`], the third choice was
competitor 4 [viz `d`], fourth choice was competitor 5 [`e`] and fifth
choice was competitor 2 [`b`].  So the rows are *ranks* (see the
discussion in `rrank.Rd`).  But it is very tempting to read the second
row of `RT` as "judge 2 placed competitor `b` in third place", which
is wrong because this is interpreting the row as an *order*.  This is
why the print method is there.

# Volvo ocean racing dataset

>>>>

### Toy dataset {-}

@@

The default print method used for `RT` as used above obscures the
internal structure of the object.  Note that it is possible to view
object `RT` directly by removing class `ranktable` with `unclass()`:

```{r viewdirect}
unclass(RT)
```

(it is easier to start by considering the second row; the first row is
a bit confusing).  Note carefully that the second row of `RT` (which
corresponds to the second judge) does *not* match the second column of
`OT`.  The way to read the second row of `RT` is as follows.  We see
the entries `1 3 4 5 2` indicating that the first choice was
competitor 1 [viz `a`], the second choice was competitor 3 [viz `c`],
the third choice was competitor 4 [viz `d`], fourth choice was
competitor 5 [`e`] and fifth choice was competitor 2 [`b`].  So the
rows are *ranks* (see the discussion in `rrank.Rd`).  But it is very
tempting to read the second row of `RT` as "judge 2 placed competitor
`b` in third place", which is wrong because this is interpreting the
row as an *order*.  This is why the print method is there.

### Volvo ocean racing dataset {-}

### 2025-02-23 inst/skating.Rmd
rewording
consistentify "time to process" information
S3 classes ordertable and ranktable

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
This document analyses Bradley-Terry strengths of the competitors in
the Ladies' Figure Skating at the 2002 Winter Olympics.  In the
package, dataframe `skating_table` is copied from Lock and Lock (see
skating.Rd for more details).  It also creates file `data/skating.rda`
which contains R objects `skating`, `skating_table`, and
`skating_maxp`.

```{r,showskating}
set.seed(0)
skating_table <- read.table("skating.txt",header=TRUE)
skating_table
```

@@

```{r,convertordertosupport}
head(ordertable2supp(skating_table))
```

@@

```{r,unconstrainedlikes, cache=TRUE}
mgv <- maxp(skating, give=TRUE, n=10)$value
mgv
mgv  - out
mgv  - max(out)
```

@@

```{r,label=saveskatingdataset}
save(skating_table,skating,skating_maxp,file="skating.rda")
```

>>>>

<font size="1"> (takes about twenty minutes to run without cache)
</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd).  This document analyses Bradley-Terry strengths of
the competitors in the Ladies' Figure Skating at the 2002 Winter
Olympics.  In the package, dataframe `skating_table` is copied from
Lock and Lock (see skating.Rd for more details).  It also creates file
`data/skating.rda` which contains R objects `skating`,
`skating_table`, and `skating_maxp`.

```{r,showskating}
set.seed(0)
skating_table <- ordertable(read.table("skating.txt", header=TRUE))
```

@@

```{r,convertordertosupport}
summary(suppfun(ordertable(skating_table)))
```

@@

```{r,unconstrainedlikes, cache=TRUE}
options(use_alabama = TRUE)
mgv <- maxp(skating, give=TRUE, n=1)$value
mgv
mgv  - out
mgv  - max(out)
```

@@

```{r,label=saveskatingdataset}
save(skating_table, skating, skating_maxp, file="skating.rda")
```

### 2025-02-23 inst/soling.Rmd
S3 classes ordertable and ranktable

To cite the `hyper2` package in publications, please use @hankin2017a.
Soling is a type of boat raced in the 2000 Summer Olympics.  Here I
analyse race data taken from
[wikipedia](https://en.wikipedia.org/w/index.php?title=Sailing_at_the_2000_Summer_Olympics_\%E2\%80\%93_Soling&oldid=945362535)
using a Plackett-Luce extension of the Bradley-Terry model.

```{r loadlib}
soling_table <- read.table("soling.txt")
soling_table
```

@@

```{r interpretsoling}
ordertable_to_ranktable(soling_table)
```

@@

```{r solingtolikelihood}
soling <- ordertable2supp(soling_table)
head(soling)
```

>>>>

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
Soling is a type of boat raced in the 2000 Summer Olympics.  Here I
analyse race data taken from
[wikipedia](https://en.wikipedia.org/w/index.php?title=Sailing_at_the_2000_Summer_Olympics_\%E2\%80\%93_Soling&oldid=945362535)
using a Plackett-Luce extension of the Bradley-Terry model.

```{r loadlib}
soling_table <- ordertable(read.table("soling.txt"))
soling_table
```

@@

```{r interpretsoling}
as.ranktable(soling_table)
```

@@

```{r solingtolikelihood}
soling <- suppfun(soling_table)
head(soling)
```

### 2025-02-23 inst/sushi.Rmd
preftable
S3 classes ordertable and ranktable

s <- exp(seq(from = log(0.9), to = log(6), len = 11))
L <- sapply(s,f)
```

@@

```{r,label=savesushidataset}
sushi_table <- a
save(sushi_table,  sushi, sushi_maxp, sushi_eq_classes, file="sushi.rda")
```

>>>>

s <- exp(seq(from = log(0.9), to = log(6), len = 2))
L <- sapply(s,f)
```

@@

```{r,label=savesushidataset}
sushi_table <- as.preftable(a)
save(sushi_table,  sushi, sushi_maxp, sushi_eq_classes, file="sushi.rda")
```
